A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-10-05 kobakian-cook.Rmd
added shortauthor to bib

In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC]. The creation of approximately equal population areas results in dramatically different square meterage of the administrative geographic units, such as states or electorates. The units are filled with colour to represent the value of the statistic for each unit [@EI]. This can lead to unequal emphasis on the statistical value of each of the geographic units. This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM]. Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics [-@abs2011]. The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states. The SA2s around Hobart stand out as more orange and red. To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.

>>>>

In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC]. The creation of approximately equal population areas results in dramatically different square meterage of the administrative geographic units, such as states or electorates. The units are filled with colour to represent the value of the statistic for each unit [@EI]. This can lead to unequal emphasis on the statistical value of each of the geographic units. This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM]. Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011. The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states. The SA2s around Hobart stand out as more orange and red. To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.

### 2020-10-05 kobakian-cook.tex
added shortauthor to bib

In many countries, residents are increasingly gathering to live in urban
areas around major cities \citep{ACTUC}. The creation of approximately
equal population areas results in dramatically different square meterage
of the administrative geographic units, such as states or electorates.
The units are filled with colour to represent the value of the statistic
for each unit \citep{EI}. This can lead to unequal emphasis on the
statistical value of each of the geographic units. This allows
choropleth map displays to misrepresent the spatial distributions of
human related statistics due to area-size bias \citep{BCM}. Figure
\ref{fig:melanoma-geo} is a choropleth map that uses colour to display
the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer
for males for each of the Statistical Areas at Level 2 (SA2) used by the
Australian Bureau of Statistics \citeyearpar{abs2011}. The Australian
choropleth map display draws attention to the expanse of light blue
areas across the rural communities in all states. The SA2s around Hobart
stand out as more orange and red. To create this choropleth map the SA2
polygons for 2011 from the Australian Bureau of Statistics.

>>>>

In many countries, residents are increasingly gathering to live in urban
areas around major cities \citep{ACTUC}. The creation of approximately
equal population areas results in dramatically different square meterage
of the administrative geographic units, such as states or electorates.
The units are filled with colour to represent the value of the statistic
for each unit \citep{EI}. This can lead to unequal emphasis on the
statistical value of each of the geographic units. This allows
choropleth map displays to misrepresent the spatial distributions of
human related statistics due to area-size bias \citep{BCM}. Figure
\ref{fig:melanoma-geo} is a choropleth map that uses colour to display
the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer
for males for each of the Statistical Areas at Level 2 (SA2) used by the
\citet{abs2011}. The Australian choropleth map display draws attention
to the expanse of light blue areas across the rural communities in all
states. The SA2s around Hobart stand out as more orange and red. To
create this choropleth map the SA2 polygons for 2011 from the Australian
Bureau of Statistics.
